AGB Stars in the IR: Physical Characteristics, Galactic Spatial Distribution, and Chemical Impact of the Milky Way AGB Population

### 2015-08-10 paper1/paper1_data.tex
Slight correction

		\begin{tabular}{l r r r r r r r r r r}
		\hline\hline
		Population & OGLE & QSO & AGN & SF & SB & LRGs & YSOs & Locus & \textbf{Total} \\ 
		\hline
		Original & 46,385 & 122,550 & 19,184 & 232,845 & 67,128 & 105,631 & 290 & 25,254 & $\mathbf{619,267}$ \\
		WISE match & 43,209 & 6,902 & 3,098 & 36,539 & 10,359 & 75,543 & 274 & 25,254 & $\mathbf{201,178}$ \\
		$W1$-3, $K_s$ saturation limit& 43,201 & 6,900 & 3,098 & 36,538 & 10,358 & 75,527 & 214 & 25,156 & $\mathbf{200,992}$ \\
		 $W1$-2 faint limit & 43,200 & 6,891 & 3,098 & 36,537 & 10,358 & 75,527 & 214 & 24,382 & $\mathbf{200,207}$  \\
		 $W1$-3 faint limit & 19,358 & 6,728 & 3,005 & 35,678 & 10,105 & 1,184 & 214 & 3,154 & $\mathbf{79,426}$  \\
		 $W1$-3, $K_s$ faint limit & 19,358 & 5,283 & 2,878 & 34,299 & 9,676 & 1,167 & 213 & 3,070 & $\mathbf{75,944}$ \\
		 $W1$-3 SNR $> 3$ & 18,995 & 5,279 & 2,876 & 34,285 & 9,673 & 1,079 & 213 & 3,056 & $\mathbf{75,456}$\\
		\hline\hline
		\end{tabular}}    
	\caption{Sample populations with respect to each reduction step. Please see section~\ref{sec:merged} for the appropriate saturation limits, faint limits, and WISE matching radii.\label{tab:reductions}}
	\end{center}

>>>>

		\begin{tabular}{l r r r r r r r r r r}
		\hline\hline
		Population & OGLE & QSO & AGN & SF & SB & LRGs & YSOs & Locus & \textbf{Total} \\ 
		\hline
		Original & 46,262 & 122,550 & 19,184 & 232,845 & 67,128 & 105,631 & 290 & 25,254 & $\mathbf{619,267}$ \\
		WISE match & 43,209 & 6,902 & 3,098 & 36,539 & 10,359 & 75,543 & 274 & 25,254 & $\mathbf{201,178}$ \\
		$W1$-3, $K_s$ saturation limit& 43,201 & 6,900 & 3,098 & 36,538 & 10,358 & 75,527 & 214 & 25,156 & $\mathbf{200,992}$ \\
		 $W1$-2 faint limit & 43,200 & 6,891 & 3,098 & 36,537 & 10,358 & 75,527 & 214 & 24,382 & $\mathbf{200,207}$  \\
		 $W1$-3 faint limit & 19,358 & 6,728 & 3,005 & 35,678 & 10,105 & 1,184 & 214 & 3,154 & $\mathbf{79,426}$  \\
		 $W1$-3, $K_s$ faint limit & 19,358 & 5,283 & 2,878 & 34,299 & 9,676 & 1,167 & 213 & 3,070 & $\mathbf{75,944}$ \\
		 $W1$-3 SNR $> 3$ & 18,995 & 5,279 & 2,876 & 34,285 & 9,673 & 1,079 & 213 & 3,056 & $\mathbf{75,456}$\\
		\hline\hline
		\end{tabular}}    
	\caption{Sample populations with respect to each reduction step. Please see section~\ref{sec:merged} for the appropriate saturation limits, faint limits, and WISE matching radii.\label{tab:reductions}}
	\end{center}
